---
title: "WGCNA ANALYSIS IN SINGLE CELL RNA !!!!"
author: "Sedat Kacar"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```

YOU WANT TO FIND PATTERNS OF GENES! YOU ARE EXACT RIGHT PLACE!!!

🔹 Step 1: LET'S INSTALL OR LOAD THE PACKAGES

```{r, message=FALSE}


library(WGCNA)
library(Seurat)

# I will use my seurat_object, u can use any of your seurat object!

rds_function(8) #Ignore this!

```
🔹 Step 2: Pseudobulk by Cluster (or Sample)

🔹 Step 2a : Filter genes does not have at least 50 counts (We will filter cells. We do not want artefacts to be lselected as pattterns. You can increase the threshold)

```{r}
# Step 1: Get raw counts
counts <- Endo_sickle@assays$RNA$counts  # or use @data if you're working with log-normalized

# Step 2: Count how many cells express each gene
gene_detected_counts <- Matrix::rowSums(counts > 0)

# Step 3: Filter genes expressed in at least 50 cells
genes_to_keep <- names(gene_detected_counts[gene_detected_counts >= 50])

# Step 4: Subset Seurat object
Endo_sickle_filtered <- subset(Endo_sickle, features = genes_to_keep)

# Step 5: Average expression per group
cluster_avg <- AverageExpression(Endo_sickle_filtered, return.seurat = FALSE)$RNA

# Step 6: Transpose for WGCNA
datExpr <- t(cluster_avg)

```

🔹 Step 4: Pick Soft-Thresholding Power


```{r}
powers = c(1:20)
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5)
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab = "Soft Threshold (power)", ylab = "Scale Free Topology Model Fit, signed R^2", type = "n")
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2], labels = powers, col = "red")
abline(h = 0.90, col = "red")  # Look for R^2 ~ 0.9

```

🔹 Step 5: Build the Network


```{r}
softPower <- 6  # Use the power where R^2 is ~0.9
net <- blockwiseModules(datExpr, power = softPower,
                        TOMType = "unsigned", minModuleSize = 30,
                        reassignThreshold = 0, mergeCutHeight = 0.25,
                        numericLabels = TRUE, pamRespectsDendro = FALSE,
                        saveTOMs = FALSE, verbose = 3)

```

🔹 Step 6: Get Module Eigengenes and Hub Genes


```{r}
moduleColors <- labels2colors(net$colors)
MEs <- net$MEs

# Identify hub genes in the turquoise module (example)
module <- 6
geneModuleMembership <- cor(datExpr, MEs, use = "p")
hubGenes <- names(sort(geneModuleMembership[, paste0("ME", module)], decreasing = TRUE))[1:33]

FeaturePlot(Endo_sickle, hubGenes, combine = FALSE)
```

🔹 Step 6a:et hub genes for all modules automatically

```{r}
hub_gene_list <- list()
for (mod in names(MEs)) {
  top_genes <- names(sort(geneModuleMembership[, mod], decreasing = TRUE))[1:33]
  hub_gene_list[[mod]] <- top_genes
}

# View top hub genes per module
hub_gene_list

```

🔹 Step 7:Plot MEs for every ME with ggplot2

```{r}
# Assume: correlation_matrix is the matrix you showed (traits in rows, MEs in columns)

# Transpose so MEs become rows if needed:
cor_df <- as.data.frame(MEs)

# Loop through each module and plot its correlation with traits
for (module in colnames(cor_df)) {
  barplot(
    cor_df[[module]],
    names.arg = rownames(cor_df),
    las = 2,
    col = "steelblue",
    ylim = c(-1, 1),
    main = paste("Module-Trait Correlation:", module),
    ylab = "Correlation"
  )
  abline(h = 0, lty = 2)
  Sys.sleep(1)  # pause between plots
}

```

🔹 Step 7b:Plot MEs for every ME with heatmap

```{r}
library(pheatmap)
pheatmap(MEs, cluster_rows = TRUE, cluster_cols = TRUE) #that is cool

```



```{r}
dim(geneModuleMembership) #genes versus ME types 
dim(MEs) #Your metadata colum vs ME_types

geneModuleMembership1 <- as.data.frame(geneModuleMembership)

```


```{r, eval=FALSE,  include=FALSE}
gh::gh("POST /user/repos", name = "Wgcna_analysis", private = FALSE) #making a new repo

```

```{r, eval=FALSE,  include=FALSE}
#use scater
#DimPlot
#plot_clusters
#SedatFunctions
#Sccustomized

```

